Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-12-07 doc/om-paper/paper.tex
down to 16 pgs.

\usepackage{graphicx}
\usepackage{alltt}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{multirow}

@@

With this machinery, we can define the semantics of faults by constraining the relationship between a message broadcast and the values received by the recipients. For a nonfaulty process that broadcasts, every recipient receives the sent message.
\begin{align*}
&nonfaulty\_constraint =\\
  &\quad \forall i, j \in \Id, t \in \mathbb{R}.\\
  &\quad\quad faults(i) = none\\
  &\quad\quad\quad \textnormal{ implies } recv(i, j, t) = send(i, j, t)
\end{align*}
\noindent
For symmetric faults, there is no requirement that the messages sent are the ones received, only that every recipient receives the same value.
\begin{align*}
&sym\_constraint =\\
  &\quad \forall i, j, k \in \Id, t \in \mathbb{R}.\\
  &\quad\quad (faults(i) = sym \textnormal{ and } broadcast(i, \{j, k\}, t, m))\\
  &\quad\quad\quad \textnormal{ implies } recv(i, j, t) = recv(i, k, t)
\end{align*}
\noindent
Byzantine faults are left completely unconstrained.

@@

$\OMH$ is designed to ensure \emph{validity} and \emph{agreement} properties under suitable hypotheses on the number and type of faults in the system. Validity states that if the general is nonfaulty, then every lieutenant outputs the value sent by the general. More formally, let the general broadcast $v \neq \ERR$, and let $l_i$ denote the output for lieutenant $i$:
%
\begin{equation}
  \tag{Validity}
    \forall \,i. \quad l_i = v
\end{equation}
%
Agreement states that each lieutenant outputs the same value. Let $l_i, l_j$ denote the outputs of lieutenants $i, j \in L$, respectively:
%
\begin{equation}
  \tag{Agreement}
    \forall \,i, j. \quad l_i = l_j
\end{equation}
%

@@

We have implemented $\OMH(1)$ (as well as the variants, described in Section~\ref{sec:modular}) in Symbolic Analysis Laboratory (SAL)~\cite{SAL}. SAL contains a suite of model-checkers. In our work, we use infinite-state (SMT-based) $k$-induction~\cite{Moura_boundedmodel,Armando-et-al}.

>>>>

\usepackage{graphicx}
\usepackage{alltt}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{multirow}
\usepackage{multicol}

@@

With this machinery, we can define the semantics of faults by constraining the relationship between a message broadcast and the values received by the recipients. For a nonfaulty process that broadcasts, every recipient receives the sent message, and for symmetric faults, there is no requirement that the messages sent are the ones received, only that every recipient receives the same value:
\noindent
\begin{multicols}{2}
\begin{align*}
&nonfaulty\_constraint =\\
  &\quad \forall i, j \in \Id, t \in \mathbb{R}.\\
  &\quad\quad faults(i) = none\\
  &\quad\quad\quad \textnormal{ implies } recv(i, j, t) = send(i, j, t)
\end{align*}\break
\noindent
\begin{align*}
&sym\_constraint =\\
  &\quad \forall i, j, k \in \Id, t \in \mathbb{R}.\\
  &\quad\quad\quad (\phantom{\textnormal{and }} faults(i) = sym\\
  &\quad\quad\quad \phantom{(}\textnormal{and } broadcast(i, \{j, k\}, t, m))\\
  &\quad\quad \textnormal{ implies } recv(i, j, t) = recv(i, k, t)
\end{align*}
\end{multicols}
\noindent
Byzantine faults are left completely unconstrained.

@@

$\OMH$ is designed to ensure \emph{validity} and \emph{agreement} properties under suitable hypotheses on the number and type of faults in the system. Validity states that if the general is nonfaulty, then every lieutenant outputs the value sent by the general. Agreement states that each lieutenant outputs the same value. More formally, Let $l_i, l_j$ denote the outputs of lieutenants $i, j \in L$, respectively, and let $v$ be the value the general broadcasts:
\noindent
\begin{multicols}{2}
\begin{equation}
  \tag{Validity}
    \forall \,i. \quad v \neq \ERR \Rightarrow l_i = v
\end{equation}\break
\begin{equation}
  \tag{Agreement}
    \forall \,i, j. \quad l_i = l_j
\end{equation}
\end{multicols}
%

%
%

@@

We have implemented $\OMH(1)$ (as well as the variants, described in Section~\ref{sec:modular}) in Symbolic Analysis Laboratory (SAL)~\cite{SAL}. SAL contains a suite of model-checkers. In our work, we use infinite-state (SMT-based) $k$-induction~\cite{}.
